\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fontawesome}
\usepackage{tikz}
\usepackage[sfdefault, medium]{roboto}
\usetikzlibrary{positioning}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{resumecolor}{RGB}{70, 130, 90}
% Sections formatting
\titleformat{\section}[runin]
{\vspace{-14pt}\bfseries\Large\color{resumecolor}} % Format for the section titles
{} % Label
{0em} % Horizontal space between label and title
{}[\color{gray}\titlerule\vspace{0pt}] %


% Ensure that generate pdf is machine-readable/ATS parsable
\pdfgentounicode=1

% Commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\experience}[1]{
    \begin{tikzpicture}[remember picture]
        \node (#1) [resumecolor,circle,fill,inner sep=3pt]{};
    \end{tikzpicture}
}
\newcommand{\resumeSubheading}[5]{
    \vspace{-2pt}
    \item[\experience{#1}]
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
             \textbf{#2} & #3 \\ \textit{\small#4} & \textit{\small #5} \\
        \end{tabular*}\vspace{1pt}}
\newcommand{\resumeSubSubheading}[2]{\item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
                                               \textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
                                                \small#1 & #2 \\
\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
\textbf{\Huge\scshape\color{resumecolor} Rama Shankar} \\
\textbf{\Large Senior Software Engineer} \\
\textit{\Large B.Tech Computer Science Engineering} \vspace{-1pt} \\
\end{center}

\begin{tabular*}{\textwidth}{@{}l@{\hspace*{\fill}}c@{\hfill}r@{}}
\fbox{\parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{%
\small
\textcolor{resumecolor}{\faPhone}\hspace*{0.2em} +91-9716.299.295 \hspace*{\fill}
\textcolor{resumecolor}{\faEnvelope}\hspace*{0.2em} \href{mailto:id.ramashankar@gmail.com}{id.ramashankar@gmail.com} \hspace*{\fill}
\textcolor{resumecolor}{\faLinkedin}\hspace*{0.2em} \href{https://linkedin.com/in/rshankar-in}{linkedin.com/in/rshankar-in}
}}
\end{tabular*}

\begin{itemize}[label=, left=0pt, itemsep=-5pt]
\item \textbf{Full-stack Software Engineer} with \textbf{10+ years} of expertise in \textbf{Data structure, Algorithms, Java, Spring, Angular, Python, AWS}, and \textbf{JavaScript}.
Experienced in \textbf{Micro-services} and \textbf{distributed systems}, contributing to complex software projects.
Proven success in \textbf{Agile} environments, implementing \textbf{TDD}, and excelling in \textbf{REST Web Services} and \textbf{Design Patterns}.
Ability to quickly learn and adapt to new environments and technologies.
\end{itemize}\vspace{-5pt}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading {a}
{GoDaddy } {2022 -- Present}
{SDE - 3 }{Gurgaon, India }
\resumeItemListStart
Developing the next-gen \textbf{E-commerce System}, leveraging \textbf{AWS cloud} for pricing and Discounting module.
\textbf{Role and Responsibilities:} Scrum master, requirement analysis, contributing to design decisions, leading development efforts, and ensuring system monitoring and maintenance.
\item Developed a data pusher service for seamless migration from legacy to new systems. Developed a data integrity test suite to ensure accuracy.
\item Developed a system ensuring consistent pricing for individual customers over time.
\resumeItemListEnd


\resumeSubheading{b}
{Ericsson Research and Development}{2018 -- 2022}
{Senior Software Engineer}{Gurgaon, India}
\resumeItemListStart
Worked on \textbf{Revenue Manager}, a cloud-native, real-time, catalog-driven solution for the telecom industry, which has all the required features like charging, billing, customer management, etc. \textbf{Role and Responsibilities are requirement analysis, design, coding, and automation testing using Junit and integration test, peer code review}
\resumeItem
{Enhanced API performance by 80 percent, resolving initial unresponsiveness with 5000 records.}
\resumeItem
{Added support of GDPR, incorporating the masking of sensitive data in logs.}
\resumeItem
{Implemented support of customer data migration APIs across multiple sites.}
\resumeItemListEnd

\resumeSubheading{c}
{Iris Software Inc}{2017 -- 2018}
{Technical Consultant}{Noida, India}
\resumeItemListStart
{Worked as consultant for banking project. Developed validation features for the product. Written automation test by using Junit and Integration testing..}
\resumeItemListEnd

\resumeSubheading{d}
{VirtusaPolaris}{2016 -- 2017}
{Associate Consultant}{Gurgaon, India}
\resumeItemListStart
{Contributed to the development of an ODS (a normalized database), playing a crucial role in its design and implementation.}
{Designed and implemented report generation features, allowing customers to conveniently download their reports on a monthly and annual basis.}
\resumeItemListEnd

\resumeSubheading{e}
{Oodles Technologies}{2013 -- 2016}
{Lead Developer}{Gurgaon, India}
\resumeItemListStart
\textbf{CaptionLabs:} Traffic management web app. Worked on modules: work order, task tracker, invoicing, and payment.
\textbf{Media Catapult:} Video streaming and content management web. Created REST APIs for IPTVS communication, analytics, and media scheduling. Implemented 24x7 virtual live broadcast streaming and live streaming.
\textbf{Contributed to product design, developed backend and frontend, maintained deployment server, and assisted junior developers}.

\resumeItem
{Led a team in the development of a peer-to-peer video communication application.
Developed a video content management and streaming application, including features for video uploading via FTP, resumable upload, VOD, and live streaming.
Developed the creation of a scheduling calendar for VOD.}
\resumeItem
{Built an online job traffic management application from the ground up, focusing on features such as job alignment, job tracking, email templates, notifications, and payment gateway integration.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\begin{tikzpicture}[remember picture,overlay]
\draw[gray, shorten >=1mm, shorten <=1mm] (a)-- (b);
\draw[gray, shorten >=1mm, shorten <=1mm] (b)-- (c);
\draw[gray, shorten >=1mm, shorten <=1mm] (c)-- (d);
\draw[gray, shorten >=1mm, shorten <=1mm] (d)-- (e);
\end{tikzpicture}

\end{document}
